\sys: Light-touch Data-Parallel Shell Processing

### 2020-10-07 paper/draft.tex
Checkpoint

\begin{figure}[t]
\centering
% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_example2.pdf}}
\begin{minted}[fontsize=\footnotesize]{bash}
mkfifo $t{0,1...}
curl $base/$y > $t0 & cat $t0 | split $t1 $t2 &
cat $t1 | xargs -n1 curl -s >$t3 & 
cat $t2 | xargs -n1 curl -s >$t4 &
...
cat $t9 | sort -rn > $t11 & cat $t10 | sort -rn > $t12 &
cat $t11 | eager > $t13 & cat $t12 | eager > $t14 &
sort -m -rn $t13 $t14 > $t15 &
cat $t15 | head -n1 > $out1 &
wait $! && ./dash_get_pids | xargs -n 1 kill -SIGPIPE
\end{minted}
\caption{
  \textbf{\sys's $2\times$-parallel output for fragment of Fig.~\ref{fig:example}.}
  \sys orchestrates the script's parallel execution through named pipes, parallel operators and careful placement of combiners.
}
\vspace{-15pt}
\label{fig:example2}
\end{figure}

@@

Often these commands do not operate in an online fashion, but need to block until the end of a stream.
A typical example of this is \ttt{sort}, which cannot start emitting results before the last input element has been consumed.
Such constraints affect task parallelism, but not data parallelism:
  \ttt{sort} can be parallelized significantly using divide-and-conquer techniques---\ie by encoding it as a group of (parallel) $map$ functions followed by an $aggregate$ that merges the results.

@@

\heading{Key Concerns}
\sys's annotations focus on three crucial concerns:
  (i) a command's parallelizability class,
  (ii) a command's inputs and outputs, and the characteristics of input consumption, and
  % (ii) for commands that support multiple inputs, the characteristics of input consumption, and
  (iii) how do flags affect a command's class, inputs, and outputs.
As the first concern was discussed extensively in the previous section, we now focus on the latter two.

@@

Command flags (options) are a particularly popular way to control a command's execution, directly affecting its parallelizability classification.
Commands are thus assigned a default parallelizability class, which should then be refined by the set of flags the command uses.
For example, \ttt{cat} defaults to \sta, but with \ttt{-n} it jumps into \pur because it has to keep track of a counter and print it along with each line.

@@

\heading{Example Annotations}
The parallelizability properties of each command are specified in an annotation record that contains several components, each addressing one of the key concerns.
On the top level, each annotation record contains a set of clauses, each one identified by a predicate on the command arguments (Concern (iii)). 
Each clause contains an assignment for the command, indicating its class (Concern (i)), and the sequence of its inputs and outputs (Concern (ii)).
%  (a JSON object) that
% Annotations treat flag arguments differently from file arguments, by checking if they start with a \ttt{-}.
% \footnote{
%   Note that the single character \ttt{-} is not an option as it is most often used to designate that a command reads from its standard input.
%   \nv{
%     There are options of of the form --f "x; y", and BSD options do not take \ttt{-} (like \ttt{ps aux}).
%     I am also not sure how important this last sentence is, as it did not answer a question I had---I expected arguments to be anything: if soneome wants to put ``pizza'' the DSL should not disallow it.
%   }
% }
% The complete annotation grammar is shown in Appendix~\ref{alg}. \str
% \kk{EuroSys doesn't allow appendix. I think we should just remove the grammar.}

@@

\heading{Complete Annotation Language}
%
The complete annotation language contains 6 operators (one of which supports regural expressions), and we used it to specify the annotation records for \todo{X} commands totalling \todo{Y} lines of JSON---an effort that took about \todo{N} hours. An important point is that annotation records can be conservative by default to not jeopardize correctness, but can be incrementally refined to capture parallelizability when using increasingly complex combinations of flags. Our language is extensible with more operators (as long as the user defines an interpreter for them) and also supports writing arbitrary python code for commands whose properties are difficult to capture, such as the higher order \ttt{xargs} whose parallelizability class depends on the class of the command that it invokes.
% \str
% \kk{Mention that some commands, such as xargs are handled internally due to their particularities.}

>>>>

\begin{figure}[t]
\centering
% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_example2.pdf}}
\begin{minted}[fontsize=\footnotesize]{bash}
mkfifo $t{0,1...}
curl $base/$y > $t0 & cat $t0 | split $t1 $t2 &
cat $t1 | xargs -n1 curl -s >$t3 & 
cat $t2 | xargs -n1 curl -s >$t4 &
...
cat $t9 | sort -rn > $t11 & cat $t10 | sort -rn > $t12 &
cat $t11 | eager > $t13 & cat $t12 | eager > $t14 &
sort-merge -rn $t13 $t14 > $t15 &
cat $t15 | head -n1 > $out1 &
wait $! && ./pash_get_pids | xargs -n 1 kill -SIGPIPE
\end{minted}
\caption{
  \textbf{\sys's $2\times$-parallel output for fragment of Fig.~\ref{fig:example}.}
  \sys orchestrates the script's parallel execution through named pipes, parallel operators and careful placement of combiners.
  \nv{Added \ttt{sort-merge}, can we sprinke more \sys primitives?}
}
\vspace{-15pt}
\label{fig:example2}
\end{figure}

@@

Often these commands do not operate in an online fashion, but need to block until the end of a stream.
A typical example of this is \ttt{sort}, which cannot start emitting results before the last input element has been consumed.
Such constraints affect task parallelism, but not data parallelism:
  \ttt{sort} can be parallelized significantly using divide-and-conquer techniques---\ie by encoding it as a group of (parallel) $map$ functions followed by a $fold$ that merges the results.

@@

\heading{Key Concerns}
\sys's annotations focus on four crucial concerns:
  (i) a command's parallelizability class,
  (ii) a command's inputs and outputs,
  (ii) for commands that support multiple inputs, the characteristics of input consumption, and
  (iii) for commands with multiple flags (options), the handling of competing sets of flags.
As the first concern was discussed extensively in the previous section, we now focus on the latter three.

@@

Command flags (options) are a particularly popular way to control a command's execution, directly affecting its parallelizability classification.
Commands are thus assigned a default parallelizability class, which is then refined by the set of flags the command uses.
For example, \ttt{cat} defaults to \sta, but with \ttt{-n} it jumps into \pur because it has to keep track of a counter and print it along with each line.

@@

\heading{Example Annotations}
The parallelizability properties of each command are specified in an annotation record (a JSON object) that
%% An annotation record
contains a set of clauses, each one identified by a predicate on the command options.
Each clause maps to an assignment for the command, indicating its class and the sequence of its inputs and outputs.
% Annotations treat flag arguments differently from file arguments, by checking if they start with a \ttt{-}.
% \footnote{
%   Note that the single character \ttt{-} is not an option as it is most often used to designate that a command reads from its standard input.
%   \nv{
%     There are options of of the form --f "x; y", and BSD options do not take \ttt{-} (like \ttt{ps aux}).
%     I am also not sure how important this last sentence is, as it did not answer a question I had---I expected arguments to be anything: if soneome wants to put ``pizza'' the DSL should not disallow it.
%   }
% }
% The complete annotation grammar is shown in Appendix~\ref{alg}. \str
% \kk{EuroSys doesn't allow appendix. I think we should just remove the grammar.}

@@

\heading{Complete Annotation Language}
%
The complete annotation language contains 6 operators (one of which supports regural expressions), and we used it to specify the annotation records for \todo{X} commands---an effort that took about \todo{N} hours. An important point is that annotation records can be conservative by default to not jeopardize correctness, but can be incrementally refined to capture parallelizability when using combinations of flags. Our language is extensible with more operators (as long as the user defines an interpreter for them) and also supports writing arbitrary python code for commands whose properties are difficult to capture, such as the higher order \ttt{xargs} whose parallelizability class depends on the class of the command that it invokes.
% \str
% \kk{Mention that some commands, such as xargs are handled internally due to their particularities.}
